---
title: "README for reproducibility check of XXXXXX (XXXX)"
author: "Student ID number"
date: "date"
output:
  html_document:
    toc: true
    toc_depth: 2

    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> This is a temaplte READme file for Assessment 1 - edit it according to below guidelines. It is based on Project TIER Protocol 4.0 (https://www.projecttier.org/tier-protocol/protocol-4-0/).

# 1. About this project

Describe what research you are replicating:

- reference to the paper your project is based on;
- claim you are focusing on and running direct replication;
- which display item (table, figure + page) and specification (e.g. model/column) your project reproduces.

# 2. Project workflow and documentation

Provide an outline of the hierarchy of folders and subfolders which are in your project folder.

List all files stored in each folder and subfolder.

# 3. Instructions for reproducing the results

Provide step-by-step instructions for using the documentation in your project folder to reproduce the results of your exact replication. For example:

- to open Rproj file first;
- if there is more than one R script, what is the order of running them;
- how to get original data;
- whether your Rproj was created with/without the `renv` package.

The instructions must be detailed and precise to make it possible for an interested user to reproduce your work without contacting you.

# 4. My enviroment

Provide information about versions of R and specific packages used to create your project. You can do it using `sessionInfo()` function.

```{r envir}
sessionInfo()
```

